BACI of biomass change for VOCC source cells for all years

### 2019-08-25 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
working multi-year BACI

---
title: "BACI of biomass change for VOCC source cells"
author: "Philina English"
date: '2019-08-22'
output: html_document
---

@@

#### Set vector type
```{r echo=TRUE}
 climate <- "temperature"
# climate <- "do"
# climate <- "do and temperature"
```

#### Make climate vectors for biannual changes between surveys
```{r echo=TRUE}
#trend <- FALSE
temp_threshold <- c(1)
do_threshold <- c(0.1)
```

# OR

#### Make climate vectors for average changes and lower threshold values
```{r echo=TRUE}
# trend <- TRUE
# temp_trend_threshold <- c(0.25)
# do_trend_threshold <- c(0.2)
```

@@

  vocc_plot <- plot_vocc(vocc,
    vec_aes = "distance",
    min_vec_plotted = input_cell_size,
    NA_label = ".",
    fill_col = "diff",
    fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
    raster_alpha = 1,
    white_zero = TRUE,
    vec_alpha = 0.25,
    axis_lables = FALSE,
    transform_col = no_trans 
  ) + ggtitle(climate)
}

@@

biomass_list <- biomass_list[!sapply(biomass_list, is.null)]

# glimpse(biomass_list)
```

Extract biomass values to match spatial and temporal range of climate vectors
```{r}

alldata <- lapply(biomass_list, function(i) {

  biomass_by_year <- list()

  for (j in seq_along(start_years)) {
   start_time <- start_years[[j]]
   end_time <- start_time + 2

   biomass_by_year[[j]] <- make_trend_data(i,
    ssid = model_ssid,
    start_time = start_time,
    skip_time = skip_time,
    end_time = end_time,
    input_cell_size = input_cell_size,
    scale_fac = scale_fac,
    delta_t_total = delta_t_total,
    delta_t_step = delta_t_step,
    indices = indices,
    variable_names = "est_exp"
  )
  }

@@

  biomass_covs <- i %>% select(X, Y, depth, trawled, muddy, any_rock, omega_s) %>% distinct()

@@

  # identify all possible control cells, assume distance = 0 given

@@

  alldata

```{r, include=FALSE, echo=FALSE}
lapply(alldata, function(i){ggplot(i, aes(x=cell_type, y=log(start_density))) + geom_boxplot()})
```

@@

ggplot(data, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = dat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(time~start_time)+
  theme_bw()
```

@@

#FIXME: need to nest random effects
gam4 <- gamm4::gamm4(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs) + (1|start_time), data=data) # + s(X,Y, bs="re")

@@

ggplot(idata, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = idat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(time~start_time)+
  theme_bw()
```

>>>>

---
title: "BACI of biomass change for VOCC source cells for all years"
author: "Philina English"
date: '2019-08-24'
output: html_document
---

@@

#### Set vector type
```{r echo=TRUE}
 climate <- "temperature"
 temp_threshold <- c(0.5)

# climate <- "do"
# do_threshold <- c(0.1)

# climate <- "do and temperature"
```

@@

  vocc_plot <- plot_vocc(vocc,
    vec_aes = "distance",
    min_vec_plotted = input_cell_size,
    NA_label = ".",
    fill_col = "diff",
    fill_label = paste("Change from\n", start_time, "to", start_time + delta_t_total, ""),
    raster_alpha = 1,
    raster_limits = c(-4, 3),
    white_zero = TRUE,
    vec_alpha = 0.25,
    axis_lables = FALSE,
    transform_col = no_trans 
  ) + ggtitle(climate)
}

@@

biomass_list <- biomass_list[!sapply(biomass_list, is.null)]
# glimpse(biomass_list)
```

Extract biomass values to match spatial and temporal range of climate vectors
```{r}
alldata <- lapply(biomass_list, function(split_bio_data) {

  biomass_by_year <- list()
  for (j in seq_along(start_years)) {
   start_time <- start_years[[j]]
   end_time <- start_time + 2

   biomass_by_year[[j]] <- make_trend_data(split_bio_data,
    ssid = model_ssid,
    start_time = start_time,
    skip_time = skip_time,
    end_time = end_time,
    input_cell_size = input_cell_size,
    scale_fac = scale_fac,
    delta_t_total = delta_t_total,
    delta_t_step = delta_t_step,
    indices = indices,
    variable_names = "est_exp"
  )
  }

@@

  biomass_covs <- split_bio_data %>% 
    select(X, Y, depth, trawled, muddy, any_rock, omega_s) %>% 
    distinct()

@@

  # identify all possible control cells have been given a distance == - dist_intercept

@@

  alldata
})
```

```{r, include=FALSE, echo=FALSE}
lapply(alldata, function(i){ggplot(i, aes(x=cell_type, y=log(start_density))) + geom_boxplot()+facet_wrap(~start_time)})
```

@@

ggplot(data, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = dat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(start_time~time)+
  theme_bw()
```

@@

gam4 <- gamm4::gamm4(as.formula(gamm_formula), random = ~(1|matchobs) + (1|origobs) + (1|start_time), data=data) # + s(X,Y, bs="re")

@@

ggplot(idata, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = idat_summary,
            aes(cell_type, max(data$log_density), label = n), hjust = -0.3) +
  facet_grid(start_time~time)+
  theme_bw()
```
